\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\large{
    {#1 \vspace{0pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\usepackage{array}

% Define a custom column type
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}} % left-aligned column with fixed width
\newcolumntype{R}{>{\raggedright\arraybackslash}X}       % right-aligned column, auto width

%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Masashi Kondo} \\ \vspace{1pt}
    \textbf{\Large \scshape Senior Software Engineer} \\
    (000)-000-0000 $|$ Vancouver, British Columbia, Canada \\
    \href{https://linkedin.com/in/masashi-kondo}{\underline{linkedin.com/in/masashi-kondo}} $|$
    \href{https://github.com/MssKnd}{\underline{github.com/MssKnd}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
As a Software Engineer with over 10 years of experience specializing in Web Frontend, I excel in developing responsive, performant, and accessible applications with React, TypeScript, and ES6. automated testing (unit, integration, E2E), semantic HTML, CI/CD (GitHub Actions), GraphQL, and progressive web apps. Adept at aligning technical solutions with business goals and driving team productivity through effective agile methodologies. Speaker at GDG DevFest 2020 Tokyo.

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {CEO / Full Stack Software Engineer (Self-employed)}{Jun 2022 -- Present}
      {Rokka LLC}{Kumamoto, Japan}
      \resumeItemListStart
        \resumeItem{Built responsive, accessible, secure, and performant web applications with React and TypeScript, implementing robust automated testing (unit, integration, E2E).}
        \resumeItem{Optimized frontend performance significantly, reducing rendering times and memory usage for mobile-first applications.}
        \resumeItem{Designed and implemented a Design System to ensure consistency and efficiency in UI/UX.}
        \resumeItem{As a Scrum Master, enhanced Scrum events' efficiency, doubling meeting productivity and improving feedback cycles, resulting in a 20\% increase in overall team productivity.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer / Web Frontend Engineer}{Dec 2018 -- Mar 2022}
      {Safie Inc.}{Tokyo, Japan}
      \resumeItemListStart
        \resumeItem{Created interactive and performant web-based video viewing applications optimized for diverse devices, including mobile, leveraging Angular and modern CSS techniques.}
        \resumeItem{Integrated frontend solutions with machine learning capabilities, demonstrating cross-domain collaboration and iterative development.}
        \resumeItem{Successfully led the adoption of Scrum during the team's growth, overseeing velocity tracking and visualization to stabilize the development process.}
      \resumeItemListEnd

    \resumeSubheading
      {Network Engineer}{Jul 2013 -- Dec 2018}
      {SoftBank Corp.}{Tokyo, Japan}
      \resumeItemListStart
        \resumeItem{Maintained dedicated line systems and developed web applications.}
        \resumeItem{Designed and implemented business systems with VPN between international offices in 2 months.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Kansei Science}{Apr 2011 -- Mar 2013}
      {Kyushu University}{}
    \resumeSubheading
      {Bachelor of Science in Information Science (Computer Science Equivalent)}{Apr 2009 -- Mar 2011}
      {Kumamoto National College of Technology}{}
  \resumeSubHeadingListEnd
  
%-----------SKILLS-----------
\section{Skills}
  \setlength{\leftskip}{0.15in}
  \begin{tabularx}{\dimexpr\textwidth-0.15in\relax}{L{2.18in} R}
    \textbf{Programming Languages:} & TypeScript, ES6, Deno, JavaScript, Kotlin, HTML/CSS \\
    \textbf{Frameworks \& Libraries:} & React, Angular, GraphQL, Next.js, jest, Storybook, Playwright, Spring boot \\
    \textbf{Tools \& Platforms:} & Git, GitHub Actions (CI/CD), Node.js, Supabase, PostgreSQL, Figma, Docker, AWS, IntelliJ IDEA, Cursor \\
    \textbf{Other:} & CSS, Accessibility (a11y), Semantic HTML, Progressive Web Apps (PWA), Web Performance Optimization, Web Standard API, Agile methodologies, Notwork Technology, Security
  \end{tabularx}

%-----------CERTIFICATIONS-----------
% \section{Certifications}
% \begin{tabularx}{\textwidth}{L{4in}@{\hskip 1em}R}
%   \textbf{・ AWS Certified Solutions Architect - Associate} & \textbf{・ Network Specialist} \\
%   \textbf{・ Applied Information Technology Engineer} & \textbf{・ ITIL FOUNDATION V3}
% \end{tabularx}

\end{document}